All_Figures_that_go_on_MS

### 2020-08-03 Scripts/All.figures.that.go.in.the.MS.reviewed.Rmd
Updated scripts

---
title: "All_Figures_that_go_on_MS"
author: "Ramon Gallego"
date: "10/30/2019"
output: html_document
editor_options: 
  chunk_output_type: inline
---

@@

```{r libraries and custom functions, echo = F, message=F}
library (RColorBrewer)
library (rstanarm)
library (fitdistrplus)
library (ggridges)
library (ggforce)
library (tidyverse)
library (cowplot)
library (concaveman)
library (vegan)
library (lubridate)
library (ggrepel)
library (factoextra)
library(nnet)
#library (OneR)
#functions for future Salish Sea
models <- readRDS("../../Analysis/Splitting.data.by.lifestyle/ModelOutputs/full_model_output_rpk_TpH.standardized_2019-08-13_1567.RDS")
source("RPK_climate_model_functions.R")

source("../../tibble.to.matrix.r")
```

@@

To begin with: the ASV.by.taxa dataset and the environmental data (Updated salinity, DIC and pH)
### Present day datasets
```{r }
data.plankton <- read_csv("../../Data/Combined_Biol_Env_Plankton.csv")

@@

env.data <- read_csv("../../Analysis/Splitting.data.by.lifestyle/env.data.for.log.regression.csv")

@@

now.env.data %>%
  gather(-Season, -sample, -Area, key = "Predictor", value = "value") %>%
  group_by(Predictor) %>%   #RPK: this was missing, which messed up the std calculations 
  mutate(std = vegan::decostand(value, method = "standardize")) -> now.env.data.with.std

# Dataset to go between standarized and real values
now.env.data.with.std %>% 
  group_by(Predictor) %>% 
  summarise(mean = mean(value),
            sd = sd(value)) %>% 
  group_by(Predictor) %>% 
  nest(params = c(mean, sd) )-> transforming.df

phylum.info <- read_csv("../../Supp.Material.OA.eDNA/Input/higher_taxonomy.csv") %>% 
  unite(family, genus, species, sep = "|", col = "taxa")

@@

```{r}
#read in observed data, which will be the starting point for adjusting in future projections          
obsData <- models$data[[1]] %>% 
  dplyr::select(Temperature, pH, Area, Season)

YearSpan <- c(2017, 2095)#seq.int(2015, 2095, 20)  #taking these individual years to model
Nyears <- length(YearSpan)
NiterationsPerYear <- 50  #number of realizations of the future environmental conditions
Nreps <- Nyears*NiterationsPerYear

#here, replicate the observed dataframe Nreps times, where Nreps = Nyears * NiterationsPerYear
simData <- obsData[rep(row.names(obsData), Nreps), 1:4] %>% 
  mutate(Year = rep(YearSpan, 
                    each = nrow(obsData)*NiterationsPerYear),
         Iteration = rep(1:NiterationsPerYear, times = nrow(obsData)*Nyears))

@@

function to generate future climate distributions isn't vectorized, so now adjust Temperature and pH for each year in a loop:
these use stochastic sampling functions r_T_year_STD() and r_pH_year_STD()

```{r}
set.seed(100)
      for (i in unique(simData$Year)){
        for (j in 1:NiterationsPerYear) {
          for (k in unique(simData$Season)) {
            for (m in unique(simData$Area)) {

              dataSubset <- simData$Temperature[simData$Year == i & 
                                                  simData$Iteration == j &
                                                  simData$Season == k &
                                                  simData$Area == m]

        simData$Temperature[simData$Year == i & 
                              simData$Iteration == j &
                                simData$Season == k &
                                  simData$Area == m] <-     #future condition is ....

                                             dataSubset +    #the current condition, plus...

                      r_T_year_STD_subset(i,  #the difference seen in the specified year
                                          length(dataSubset),  
                                          2017, # standardized to reference year
                                          season = k,
                                          area = m)

        simData$pH[simData$Year == i & 
                              simData$Iteration == j &
                              simData$Season == k &
                              simData$Area == m] <-     #future condition is ....
          simData$pH[simData$Year == i & 
                                simData$Iteration == j &
                                simData$Season == k &
                                simData$Area == m] +    #current condition, plus...

          r_pH_year_STD_subset(i,  #the difference seen in the specified year
                              10,  
                              2017, # standardized to reference year
                              season = k,
                              area = m)[1] #one draw per iteration for the simulated set of temperatures
          } 
         }
        }
      }

### Convert standardized units to natural units using reference year

```{r}
#observed = (std * SD) + mean

#useful later:
reference_Temperature_SD <- sd(now.env.data$Temperature)
reference_Temperature_mean <- mean(now.env.data$Temperature)
reference_pH_SD <- sd(now.env.data$pH)
reference_pH_mean <- mean(now.env.data$pH)

simData <- simData %>% 
  rename(TemperatureSTD = Temperature,
        pH_STD = pH) %>% 
  mutate(TemperatureCelsius = (TemperatureSTD * reference_Temperature_SD) + reference_Temperature_mean,
         pH_units = (pH_STD * reference_pH_SD) + reference_pH_mean)

#check that this is perfectly linear
# simData %>%
#   ggplot(aes(x = TemperatureSTD, y = TemperatureCelsius)) +
#   geom_point()

#check for trends
# simData %>% 
#   select(Year, Season, Area, TemperatureCelsius) %>% 
#   group_by(Year, Season, Area) %>% 
#   summarize(mean(TemperatureCelsius))
```
If we look at this data, does it have crazy points
```{r limits}
simData %>% 
  group_by(Year, Season, Area) %>% 
  summarise_at(c("TemperatureCelsius", "pH_units"), .funs = list(min = min, max = max))

# Yep, a bit crazy. Apply 90% interval

simData %>%
  group_by(Year, Area) %>% 
  nest() %>% 
  mutate(
    values = map (data, function (.x) {
      list(temp = fitdistr(.x$TemperatureCelsius ,
             densfun = "normal"),
           ph = fitdistr(.x$pH_units ,
             densfun = "normal"))
            }
          ),

    data = map2(data,values,  function (.x, .y){
      .x %>%
        mutate(pT = pnorm(TemperatureCelsius, mean  = .y[["temp"]]$estimate[1], sd = .y[["temp"]]$estimate[2]),
               ppH =pnorm(pH_units, mean  = .y[["ph"]]$estimate[1], sd = .y[["ph"]]$estimate[2]) )

    })
    ) %>% 
  unnest(data) %>% 
  mutate(keep = case_when(pT < 0.1 | ppH < 0.05 | pT > 0.9 | ppH > 0.9 ~ "Discard",
                          TRUE                   ~ "keep")) %>% 
  filter (keep == "keep")-> simData.nocrazys
simData.nocrazys %>%
  rename(Temperature = TemperatureSTD,
         pH = pH_STD) %>% 
saveRDS( file = "../../Analysis/Splitting.data.by.lifestyle/all.sim.data_climateScenarios_no.outliers.RDS")
simData.nocrazys %>% 
  group_by( Area, Season) %>% 
  summarise_at(c("TemperatureCelsius", "pH_units"), .funs = list(min = min, max = max))

@@

### Panel A Sample location
```{r Base map}
map <- readRDS("map.plot.rds")

@@

```{r}
boxplot.richness <- readRDS("richness.rds")

@@

plot_grid(bottom.plot, ridges,
          align = "h",
          nrow = 2,
          rel_heights = c(0.6, 0.4),
          labels = c(NA,"C")) +
  ggsave(filename = "Fig1.png", width = 14, height = 14, dpi = "retina")

@@

data.plankton %>% 
  separate (event, into = c("Site", "Date"), sep = "_") %>% 
  mutate(Season = case_when(str_detect(Date,"17-03|17-10|17-11|18-01|18-03") ~ "Winter",
                             TRUE ~                                         "Summer"),
         Area = case_when(Site %in% c("CP","LK", "FH") ~ "San Juan Island",
                          TRUE                         ~ "Hood Canal")) %>% 
   unite (Site, Date, col = "event", sep = "_") %>% 
  cap.functions.only3things(Area, Season) -> joined.dataset.for.CAP
```
Use the functions
```{r lets CAP this}
joined.dataset.for.CAP %>% 
 # select(DIC = mean.DIC.new.sal, Salinity = Salinity.new, Temperature, pH = pH_new, everything())
  raw.PCAs  %>% 
  mutate(Titles = paste(Area,Season, sep = " - " )) -> Clusters.analysis.and.cap
```

@@

Clusters.analysis.and.cap %>% 
  select(Area, Season, full.cluster.info) %>% 
  unnest() %>% #filter (Area == "Hood Canal", Season == "Summer") %>% 
  write_csv("../../Analysis/Splitting.data.by.lifestyle/clusters.of.events.csv")
Clusters.analysis.and.cap %>% pull(Final.plot2) 
```

@@

clusters <- read.csv("../../Analysis/Splitting.data.by.lifestyle/clusters.of.events.csv") %>% 
  filter(Season == "Summer",
         Area == "Hood Canal")
  clusters$cluster <- as.factor(clusters$cluster)
```

@@

# right_top + coord_equal () -> right_top 
 ggsave("Figure2.topright.png", width = 7)
```

@@

clusters.all <- read.csv("../../Analysis/Splitting.data.by.lifestyle/clusters.of.events.csv")

@@

```{r}
simData.nocrazys %>% 
  mutate(Area = case_when(Area == "SJI" ~ "San Juan Island",
                          TRUE          ~ Area)) %>% 
  group_by( Area, Season) %>% 
  summarise_at(c("TemperatureCelsius", "pH_units"), .funs = list(min = ~ min(round(.x, 1)), max = ~max(round(.x, 1)))) %>% 
  group_by (Season, Area) %>% 
  nest() %>% 
  mutate(data = map (data, ~ expand_grid(Temperature = seq(round(.x$TemperatureCelsius_min,1), round(.x$TemperatureCelsius_max, 1),by = 0.1),
                                         pH_new = seq(round(.x$pH_units_min,1), round(.x$pH_units_max,1), by = 0.1)))) -> limits.for.planb

@@

  simper2 %>% 
    group_by(comparison) %>% 
    nest() %>% 
    mutate(data = map (data, ~ .x %>% bind_cols(SIMPER.clusters %>% 
                                                filter (Area == "Hood Canal", Season == "Summer") %>%
                                                ungroup() %>% 
                                                select(taxa.simper) %>% 
                                                unnest()))) %>% 
    unnest(data) %>% 
  filter (p < 0.05) %>% 
  write_csv("../../Analysis/Splitting.data.by.lifestyle/simper.HoodCanal.summer.csv")

## Get the data for all seasons and areas
 SIMPER.clusters %>%
   pull(summary.simper)-> list.of.simpers

 list.of.simpers %>% 
   map_df(~bind_rows(.x, .id = 'Comparison'), .id = 'var1') %>%
   separate(var1, into = c("Area", "Season"), sep = "_") %>%
   group_by(Area, Season, Comparison) %>% 
   nest() %>% 
   left_join(SIMPER.clusters) %>%
   mutate(data = map2(data, taxa.simper, ~bind_cols(.x, as_tibble(.y)))) %>% 
   select(Area, Season, Comparison, data) %>% 
   unnest(data) %>% 
  # rename(taxa = value) %>% 
  write_csv("../../Analysis/Splitting.data.by.lifestyle/simper.all.csv")

```
#### Now do the dreamed panel
```{r}
taxa.to.follow <- read_csv("../../Analysis/Splitting.data.by.lifestyle/simper.HoodCanal.summer.csv")

@@

all.taxa.to.follow <- read_csv("../../Analysis/Splitting.data.by.lifestyle/simper.all.csv")

@@

ggsave(filename = paste0("Figure2.", Sys.Date(), ".png"),
         width = 14,height = 5, dpi = "retina")

@@

list.of.right.plots

@@

pmap(.l = list(top.plots.in.a.list, list.of.legends, list.of.labels),
     .f = function(a,b,c) plot_grid(a,b, align = "v", nrow = 2, rel_heights = c(1, 0.1), labels = c) +
       ggsave(filename = paste0(c,"CAP.plot.png"),  width = 14,height = 5, dpi = "retina")) -> plots.ready.to.go

plots.ready.to.go %>% saveRDS("All_Cap_for_suppplemental.rds")
```

@@

```{r}
## Rename variables so the model can be projected

all.sims.for.projection <- simData.nocrazys %>% 
  rename(Temperature = TemperatureSTD,
         pH = pH_STD)

@@

posterior.draws.all %>% 
 left_join(phylum.info %>% dplyr::select(phylum, taxa)) %>% 
  group_by(phylum) %>% # Add phylum information
  nest() %>% 
  mutate (data = map (data, ~ .x %>% 
                        unnest() %>% 
                        pivot_longer(cols = c(-taxa, -sim.row),
                                    names_to = "draw.row", values_to = "presence") %>% 
  group_by(taxa, sim.row) %>% 
  summarise(prob.of.presence = mean(presence)) %>% 
  left_join(all.sims.for.projection %>%  
              rownames_to_column("sim.row")) 
  #filter (Year %in% c(2015, 2095))
  )) -> posterior.probabilities.by.taxa

posterior.probabilities.by.taxa %>% mutate(suma = map (data,~.x %>% group_by(taxa, Year) %>% summarise(tot = sum(prob.of.presence)) %>% ungroup() %>% 
                                                         pivot_wider(names_from = Year, values_from = tot) %>% 
                                                         group_by(taxa) %>% mutate(diff = `2017` - `2095`))) %>% select(phylum, suma) %>% unnest(suma) %>% arrange(desc(abs(diff))) %>% 
  filter (phylum %in% c("Bacillariophyta", "Dinophyceae", "Haptophyceae", "Arthropoda"))

posterior.probabilities.by.taxa %>% 
  mutate( plot.by.taxa = map2 (data, phylum, ~ .x %>% 
      separate(taxa, into = c("family","genus", "species"), sep = "\\|", remove = F) %>%
  mutate(label = case_when((species == "NA" & genus == "NA") ~ paste0(family, " sp."),
                           species == "NA" ~  paste0(genus, " sp."),
                           TRUE            ~ species))    %>% 
    mutate(Area = case_when(Area == "SJI" ~ "San Juan Island",
                            TRUE          ~ Area)) %>%

  ggplot(aes(x= prob.of.presence,
             y = label)) +
  #geom_density_ridges(fill = as.factor(Year))
  stat_density_ridges(aes(fill = as.factor(Year)),
    # geom = "density_ridges_gradient", calc_ecdf = TRUE,
    quantiles =2, quantile_lines = TRUE, alpha = 0.5
  ) + 
  scale_fill_brewer(name = "Year",  type = "qual", palette = 2) + 
  labs (x = "Probability of presence",
        y = "") +
    facet_wrap(~Area) +

>>>>

---
title: "All_Figures_that_go_on_MS"
author: "Ramon Gallego"
date: "10/30/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

@@

```{r libraries and custom functions, echo = F, message=F}
library (RColorBrewer)
library (rstanarm)
library (fitdistrplus)
library (ggridges)
library (ggforce)
library (tidyverse)
library (cowplot)
library (concaveman)
library (vegan)
library (lubridate)
library (ggrepel)
library (factoextra)
library (nnet)
library (here)
library (conflicted)
conflict_prefer("filter", "dplyr")
conflict_prefer("select", "dplyr")
#functions for future Salish Sea
models <- readRDS(here("Input","full_model_output_rpk_TpH.standardized_nonSeasonal2020-06-24_3262.RDS"))
source(here("Scripts","RPK_climate_model_functions_REVISIONS.R"))

source(here("Scripts","tibble.to.matrix.r"))

stds_to_value <- read_rds(here("Input", "std_to_real.rds"))

@@

To begin with: the ASV.by.taxa dataset and the environmental data (Updated salinity, DIC and pH)
### Present day datasets
```{r }
data.plankton <- read_csv(here("Input","Combined_Biol_Env_Plankton.csv"))

@@

env.data <- read_csv(here("Input","env.data.for.log.regression.csv"))

@@

now.env.data %>%
  gather(-Season, -sample, -Area,  key = "Predictor", value = "value") %>%
  group_by(Area, Predictor) %>%   #RPK: this was missing, which messed up the std calculations 
  mutate(std = vegan::decostand(value, method = "standardize")) -> now.env.data.with.std

#### TODO: remove

# Dataset to go between standarized and real values
now.env.data.with.std %>%
  group_by(Area, Predictor) %>%
  # summarise(mean = mean(value),
  #           sd = sd(value)) %>%
  # group_by(Area, Predictor) %>%
  nest() %>% 
  summarise(tovalue = map(data, ~ lm(value ~ std, data = .x) ),
            tostd   = map(data, ~ lm(std ~ value, data = .x)))-> transforming.df

transforming.df[1,4] %>% pull -> test
broom::tidy(test[[1]])
extract <- function (lm) {broom::tidy(lm)$estimate}

extract(test[[1]])

transforming.df %>% 
  mutate(to.values = map(tovalue, extract),
         to.std= map(tostd, extract)) ->transforming.df

phylum.info <- read_csv(here("Input","higher_taxonomy.csv")) %>% 
  unite(family, genus, species, sep = "|", col = "taxa")

@@

```{r}
Year.area.dataset <- function(Area, Year, n){

    Temp.conv <- stds_to_value[which (stds_to_value$Area == Area & stds_to_value$key == "Temperature"),"toValue"] %>% pull %>% .[[1]]
    pH.conv   <- stds_to_value[which (stds_to_value$Area == Area & stds_to_value$key == "pH")         ,"toValue"] %>% pull %>% .[[1]]

    one<-  data.frame(
              Area = Area,
              Year = Year,
              Temperature = r_Temperature_year_STD(Year, Area, n, 2017),
              pH          = r_pH_year_STD(Year, Area, n, 2017)
              )

    one$TemperatureCelsius = sapply(one$Temperature,function(x){Temp.conv$coefficients[1]+Temp.conv$coefficients[2]*x})
    one$pH_units            = sapply(one$pH,function(x){pH.conv$coefficients[1]+pH.conv$coefficients[2]*x})

    return(one)

}

j <- Year.area.dataset("Hood Canal", 2095, 5000)
k <- Year.area.dataset("Hood Canal", 2017, 5000)
l <- Year.area.dataset("SJI", 2095, 5000)
m <- Year.area.dataset("SJI", 2017, 5000)

simulated.scenario <- rbind(j,k,l,m)

rm(j,k,l,m)

simulated.scenario %>%
  group_by(Year, Area) %>% 
  nest() %>% 
  mutate(
    values = map (data, function (.x) {
      list(temp = fitdistr(.x$TemperatureCelsius ,
             densfun = "normal"),
           ph = fitdistr(.x$pH_units ,
             densfun = "normal"))
            }
          ),

    data = map2(data,values,  function (.x, .y){
      .x %>%
        mutate(pT = pnorm(TemperatureCelsius, mean  = .y[["temp"]]$estimate[1], sd = .y[["temp"]]$estimate[2]),
               ppH =pnorm(pH_units, mean  = .y[["ph"]]$estimate[1], sd = .y[["ph"]]$estimate[2]) )
      })
    ) %>% 
  unnest(data) %>% 
  mutate(keep = case_when(pT < 0.05 | ppH < 0.05 | pT > 0.95 | ppH > 0.95 ~ "Discard",
                          TRUE                   ~ "keep")) %>% 
  filter (keep == "keep")-> simData.nocrazys

simData.nocrazys %>% 
  select(-values) %>% write_csv("Output/simulation.from.std.functions.cleaned.csv")
```

### Save future scenarios

simData.nocrazys %>%

saveRDS( file = here("Output","all.sim.data_climateScenarios_no.outliers.RDS"))

simData.nocrazys %>% 
  group_by( Area, Year) %>% 
  summarise_at(c("TemperatureCelsius", "pH_units"), .funs = list(min = min, max = max))

@@

### Seasonality

To proyect the different community clusters fate into the pH - Temperature continuum, we need to include the seasonality or ditch it from the CAP Analysis. Here I am 
Now create a seasonal data, we can sample each year's data and select them with the profile for the seasonal data in the real dataset. By calculating the quantiles of the Temperature distributions, we see that both in the San Juan Islands and the Hood Canal, the Winter months occupy the lower 30% quantile of the data. In order to create a matrix of possible ranges of pH and Temperature for each season in the future scenario, we will apply these quantiles to the simulated data

```{r}
simData.nocrazys %>% 
  mutate(Season = case_when(pT < 0.3 ~ "Winter",
                            TRUE     ~ "Summer")) %>% 
  ggplot(aes(x = TemperatureCelsius, fill = Season)) +
  geom_density_ridges_gradient(aes(y = as.factor(Year))) +
  facet_wrap(~Area, nrow = 2)
```

Now get the ranges and create the grid for each season / Area

```{r get the ranges}

simData.nocrazys %>% 
  mutate(Season = case_when(pT < 0.3 ~ "Winter",
                            TRUE     ~ "Summer")) %>% 
  group_by(Area, Season) %>% 
  summarise_at (c("TemperatureCelsius", "pH_units"), .funs = list(min = min, max = max)) -> seasonal.ranges
```

```{r}
simData.nocrazys %>% 
  select(Area, Temperature, pH, Year) %>% 
  pivot_longer(cols = c(pH, Temperature), names_to = "Predictor", values_to = "value") -> simData.nocrazys.long

 simTemp <- r_T_year_STD(2017, 1000, 2017) %>% 
    sort()
  #what quantile of the simulated data is each of the observed points in?
  simECDF <- ecdf(simTemp) #create ecdf function from sim distribution, then find quantile for each observed point
quantile_df <- function(x, probs, na.rm =F, names = F, type = 7, ...){
  z <- quantile(x, probs, na.rm, names, type)
  output <- tibble(id = probs,
                       values = z)

      return(output)   
}

 models$data[[1]] %>% 
    select(-sample, -Noccur, -phylum, -binary) %>% 
    pivot_longer(cols = c(-Season, -Area),names_to = "Predictor", values_to = "value") %>% 
    filter (Predictor == "Temperature") %>% 
   group_by(Season, Area, Predictor) %>%
    nest()-> testdata

testdata %>% 
  unnest(data) %>% ungroup() %>% 
  select(-Season) %>% 
  group_by(Area, Predictor) %>% 
  nest(value) %>% 
  mutate(Season = "All") %>% 
  bind_rows(testdata, .) %>%

  mutate(
    betas = map(data, function(.x){
      pull(.x) %>% 
      sort() %>% 
        simECDF() %>% 
        fitdist("beta")}),
    quantiles = map (data,  ~ quantile_df(.x$value, probs = c(0, 0.25, 0.5, 0.75, 1)))) -> testdata

testdata %>% 
  left_join(transforming.df %>% select(Area, Predictor, to.values)) %>% 
  mutate(quantiles = map2(quantiles, to.values, ~.x %>% 
                       mutate(real = .y[1]+.y[2]*values ))) %>% 
# unnest(quantiles) %>% 
#   select(-values) %>% 
#   pivot_wider(names_from = id, values_from = real) %>% 
#   filter(Predictor == "Temperature") %>% 
#   arrange(Area)
  nest(-Area) %>% 
  expand_grid(., Year = c(2017, 2095)) %>% 
  unnest(data) %>% 
  nest_join(simData.nocrazys.long, by = c("Area","Predictor", "Year"), name = "new") %>% 
  mutate(lims = map2(new, betas,
                     function(.x, .y){
                       .x %>%
                         pull(value) %>% 
                         sort() -> temps 
          base::sample(temps, 
                       size = 500, 
                       replace = TRUE, 
                       prob = rbeta(length(temps), shape1 = .y$estimate[1], shape2 =.y$estimate[2])) -> temps

          quantile_df(temps, probs = c(0,0.2, 0.5, 0.7, 1))
          } )) %>%

  mutate(lims.real = map2(lims, to.values, ~.x %>% 
                       mutate(real = .y[1]+.y[2]*values ))) %>% 
# unnest(lims.real) %>% 
  unnest(quantiles) %>% 
  select(-values) %>% 
  pivot_wider(names_from = id, values_from = real)
```

@@

### Panel A Sample location
```{r Base map}
map <- readRDS(here("Input","map.plot.rds"))

@@

```{r}
boxplot.richness <- readRDS(here("Input","richness.rds"))

@@

plot_grid(bottom.plot, ridges,
          align = "h",
          nrow = 2,
          rel_heights = c(0.6, 0.4),
          labels = c(NA,"C")) +
  ggsave(filename = here("Figures","Fig1.png"), width = 14, height = 14, dpi = "retina")

@@

data.plankton %>% 
  separate (event, into = c("Site", "Date"), sep = "_") %>% 
  mutate(Season = case_when(str_detect(Date,"17-03|17-10|17-11|18-01|18-03") ~ "Winter",
                             TRUE ~                                         "Summer"),
         Area = case_when(Site %in% c("CP","LK", "FH") ~ "San Juan Island",
                          TRUE                         ~ "Hood Canal")) %>% 
   unite (Site, Date, col = "event", sep = "_") %>% 
  cap.functions.only3things(Area, Season) -> joined.dataset.for.CAP
```
Use the functions
```{r lets CAP this}
joined.dataset.for.CAP %>% 
  ungroup %>% 
 # select(DIC = mean.DIC.new.sal, Salinity = Salinity.new, Temperature, pH = pH_new, everything())
  raw.PCAs  %>% 
  mutate(Titles = paste(Area,Season, sep = " - " )) -> Clusters.analysis.and.cap
```

@@

Clusters.analysis.and.cap %>% 
  select(Area, Season, full.cluster.info) %>% 
  unnest() %>% #filter (Area == "Hood Canal", Season == "Summer") %>% 
  write_csv(here("Output","clusters.of.events.csv"))
Clusters.analysis.and.cap %>% pull(Final.plot2) 
```

@@

clusters <- read.csv(here("Input","clusters.of.events.csv")) %>% 
  filter(Season == "Summer",
         Area == "Hood Canal")
  clusters$cluster <- as.factor(clusters$cluster)
```

@@

# right_top + coord_equal () -> right_top 
 ggsave(here("Figures","Figure2.topright.png"), width = 7)
```

@@

clusters.all <- read.csv(here("Input","clusters.of.events.csv") )

@@

```{r}
simData.nocrazys %>% 
  ungroup %>% 
  mutate(Area = as.character(Area),
         Area = case_when(Area == "SJI" ~ "San Juan Island",
                          TRUE          ~ Area)) %>% 
  group_by( Area) %>% 
  summarise_at(c("TemperatureCelsius", "pH_units"), .funs = list(min = ~ min(round(.x, 1)), max = ~max(round(.x, 1)))) %>% 
  group_by (Season, Area) %>% 
  nest() %>% 
  mutate(data = map (data, ~ expand_grid(Temperature = seq(round(.x$TemperatureCelsius_min,1), round(.x$TemperatureCelsius_max, 1),by = 0.1),
                                         pH_new = seq(round(.x$pH_units_min,1), round(.x$pH_units_max,1), by = 0.1)))) -> limits.for.planb

@@

  simper2 %>% 
    group_by(comparison) %>% 
    nest() %>% 
    mutate(data = map (data, ~ .x %>% bind_cols(SIMPER.clusters %>% 
                                                filter (Area == "Hood Canal", Season == "Summer") %>%
                                                ungroup() %>% 
                                                select(taxa.simper) %>% 
                                                unnest()))) %>% 
    unnest(data) %>% 
  filter (p < 0.05) %>% 
  write_csv(here("Output","simper.HoodCanal.summer.csv"))

## Get the data for all seasons and areas
 SIMPER.clusters %>%
   pull(summary.simper)-> list.of.simpers
names(list.of.simpers) <- paste(SIMPER.clusters$Area, SIMPER.clusters$Season, sep = "_")

 list.of.simpers %>%
  map(~ .x %>% map(~ bind_rows(.)) %>% 
                          bind_rows(., .id = "Comparison")) %>% 
  bind_rows(., .id = "var1") %>%
   separate(var1, into = c("Area", "Season"), sep = "_") %>%
   group_by(Area, Season, Comparison) %>% 
   nest() %>% 
   left_join(SIMPER.clusters) %>%
   mutate(data = map2(data, taxa.simper, ~bind_cols(.x, as_tibble(.y)))) %>% 
   select(Area, Season, Comparison, data) %>% 
   unnest(data) %>% 
  # rename(taxa = value) %>% 
  write_csv(here("Output","simper.all.csv") )

```
#### Now do the dreamed panel
```{r}
taxa.to.follow <- read_csv(here("Output","simper.HoodCanal.summer.csv"))

@@

all.taxa.to.follow <- read_csv(here("Output","simper.all.csv"))

@@

ggsave(filename = here("Figures",paste0("Figure2.", Sys.Date(), ".png")),
         width = 14,height = 5, dpi = "retina")

@@

list.of.right.plots
Clusters.analysis.and.cap %>% 
  mutate (label = paste (Area, Season, sep = " ")) %>% 
  pull(label) -> list.of.labels

@@

pmap(.l = list(top.plots.in.a.list, list.of.legends, list.of.labels),
     .f = function(a,b,c) plot_grid(a,b, align = "v", nrow = 2, rel_heights = c(1, 0.1), labels = c) +
       ggsave(filename = here("Figures",paste0(c,"CAP.plot.png")),  width = 14,height = 5, dpi = "retina")) -> plots.ready.to.go

plots.ready.to.go %>% saveRDS(here("Output","All_Cap_for_suppplemental.rds"))
```

@@

We use the climate projection to predict changes in suitability

all.sims.for.projection <- simData.nocrazys %>% 
  select(Area, Year, Temperature, TemperatureCelsius, pH, pH_units)

@@

posterior.draws.all %>% 
 left_join(phylum.info %>% dplyr::select(phylum, taxa)) %>% 
  group_by(phylum) %>% # Add phylum information
  nest() %>% 
   mutate (data = map (data, ~ .x %>% 
                        unnest() %>% 
                        pivot_longer(cols = c(-taxa, -sim.row),
                                    names_to = "draw.row", values_to = "presence") %>% 
  group_by(taxa, sim.row) %>% 
  summarise(prob.of.presence = mean(presence)) %>% 
  left_join(all.sims.for.projection %>%  
              rownames_to_column("sim.row")) 
  #filter (Year %in% c(2015, 2095))
  )) -> posterior.probabilities.by.taxa
```
Now we have a nested dataframe per each phylum. Not that we need it. But the nested part is a dataframe with the mean result of the 100 draws for each environmental point.

```{r subset of taxa for manuscript}
## Now create a set of phyla and taxa to show on figure 3

posterior.probabilities.by.taxa %>%
  mutate(suma = map (data,~.x %>% group_by(taxa, Year) %>%
                       summarise(tot = sum(prob.of.presence)) %>%
                       ungroup() %>% 
                       pivot_wider(names_from = Year, values_from = tot) %>% 
                       group_by(taxa) %>% mutate(diff = `2017` - `2095`))) %>% 
  select(phylum, suma) %>% 
  unnest(suma) %>%
  arrange(desc(abs(diff))) %>% 
  filter (phylum %in% c("Bacillariophyta", "Dinophyceae", "Haptophyceae", "Arthropoda")) %>% 
  group_by(phylum) %>% 
  slice(1:5) %>% 
  pull(taxa)-> taxa.for.Fig3

posterior.probabilities.by.taxa %>%
  mutate(suma = map (data,~.x %>% group_by(taxa,Area, Year) %>%
                       summarise(tot = sum(prob.of.presence)) %>%
                       ungroup() %>% 
                       pivot_wider(names_from = Year, values_from = tot) %>% 
                        group_by(taxa) %>% mutate(diff = `2017` - `2095`)
                     )) %>% 
  select(phylum, suma) %>% 
  unnest(suma) %>%
 # arrange(desc(abs(diff))) %>% 
  group_by(phylum) %>% 
  arrange(desc(abs(diff))) %>%
  slice(1:5) %>% 
  ggplot(aes(x = fct_reorder(phylum,abs(diff)), y = abs(diff))) +
  geom_boxplot()+
  geom_point(aes(color = diff>0)) +
  coord_flip()

posterior.probabilities.by.taxa %>%
  mutate(suma = map (data,~.x %>% group_by(taxa,Area, Year) %>%
                       summarise(tot = sum(prob.of.presence)) %>%
                       ungroup() %>% 
                       pivot_wider(names_from = Year, values_from = tot) %>% 
                        group_by(taxa) %>% mutate(diff = `2017` - `2095`)
                     )) %>% 
  select(phylum, suma) %>% 
  unnest(suma) %>%
 # arrange(desc(abs(diff))) %>% 
  group_by(phylum) %>% 
  arrange(desc(abs(diff))) %>%
  slice(1:5) %>% 
  ungroup() %>% 
  filter(phylum %in% c("Bacillariophyta", "Dinophyceae", "Haptophyceae", "Chlorophyta")) %>% 
  distinct(taxa) %>% 
  pull() -> taxa.for.Fig3.2
```

```{r plotting them}
### some for fig3 ### 
posterior.probabilities.by.taxa %>% 
  filter (phylum %in% c("Bacillariophyta", "Dinophyceae", "Haptophyceae", "Arthropoda")) %>% 
  mutate( plot.by.taxa = map2 (data, phylum, ~ .x %>% 
                                 filter(taxa %in% taxa.for.Fig3) %>% 
      separate(taxa, into = c("family","genus", "species"), sep = "\\|", remove = F) %>%
  mutate(label = case_when((species == "NA" & genus == "NA") ~ paste0(family, " sp."),
                           species == "NA" ~  paste0(genus, " sp."),
                           TRUE            ~ species))    %>% 
    mutate(Area = case_when(Area == "SJI" ~ "San Juan Island",
                            TRUE          ~ Area)) %>% 
    mutate(Year = fct_rev(as.factor(Year) )) %>%

  ggplot(aes(x= prob.of.presence,
             y = label)) +
  #geom_density_ridges(fill = as.factor(Year))
  # stat_density_ridges(aes(fill = as.factor(Year)),
  #    geom = "density_ridges_gradient", calc_ecdf = TRUE,
  #   quantiles =2, quantile_lines = TRUE, alpha = 0.5
  # ) +
    geom_violin(aes(fill= (Year)), weight = 2, adjust = .5, draw_quantiles =  0.5)+
# stat_summary(fun.y=mean, geom="line", aes(group=Year)) +
  scale_fill_brewer(name = "Year",  type = "qual", palette = 4, direction = 1, breaks=c("2017","2095")) + 
  labs (x = "Probability of presence",
        y = "") +
    facet_wrap(~Area) +

 # facet_grid(phylum ~ Area) + coord_flip(xlim = c(0,1)) +
 theme(strip.text.y = element_text(angle = 0),
       axis.text.y = element_text(face = "italic")) +
   ggtitle(.y) +
  theme(legend.direction = "horizontal",
        legend.position  = "bottom") ))   -> list.of.plots.for.fig3

#A new subset to high;ight change

posterior.probabilities.by.taxa %>% 
  filter (phylum %in% c("Bacillariophyta", "Dinophyceae", "Haptophyceae", "Chlorophyta")) %>% 
  mutate( plot.by.taxa = map2 (data, phylum, ~ .x %>% 
                                 filter(taxa %in% taxa.for.Fig3.2) %>% 
      separate(taxa, into = c("family","genus", "species"), sep = "\\|", remove = F) %>%
  mutate(label = case_when((species == "NA" & genus == "NA") ~ paste0(family, " sp."),
                           species == "NA" ~  paste0(genus, " sp."),
                           TRUE            ~ species))    %>% 
    mutate(Area = case_when(Area == "SJI" ~ "San Juan Island",
                            TRUE          ~ Area)) %>% 
    mutate(Year = fct_rev(as.factor(Year) )) %>%

  ggplot(aes(x= prob.of.presence,
             y = label)) +
  #geom_density_ridges(fill = as.factor(Year))
  # stat_density_ridges(aes(fill = as.factor(Year)),
  #    geom = "density_ridges_gradient", calc_ecdf = TRUE,
  #   quantiles =2, quantile_lines = TRUE, alpha = 0.5
  # ) +
    geom_violin(aes(fill= (Year)), weight = 2, adjust = 1, draw_quantiles =  0.5, scale = "count")+
# stat_summary(fun.y=mean, geom="line", aes(group=Year)) +
  scale_fill_brewer(name = "Year",  type = "qual", palette = 4, direction = 1, breaks=c("2017","2095")) + 
  labs (x = "Probability of presence",
        y = "") +
    facet_wrap(~Area) +

  theme_minimal() +
